### 2022-11-24 dissertation/chapters/07-methodology.tex
✨ (final-review): Up to chapter 4

\begin{quotation}
      \noindent ``Observation, reason and experimentation make up what we call the scientific method.''
\end{quotation}
\begin{flushright}
      - Richard P. Feynman
\end{flushright}

\noindent
So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}. Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters. Scientific experimentation can now be conducted. Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation. The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics. This chapter provides the detailed specification of the methodology that is followed for the empirical process. Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions. The process by which the results are statistically analysed are also presented. The remainder of the chapter is structured as follows.

@@

\noindent
These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered. The empirical process is designed to answer these questions. The empirical process is structured as follows.

@@

\noindent
Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.

@@

\noindent
For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training. The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.

@@

\noindent
Note that from Table \ref{tab:methodology:heuristics}, values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it. The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.

@@

\noindent
In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm. The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.

@@

\noindent
In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}. The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.

@@

\noindent
In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only meta-heuristics are included.

>>>>

\begin{quotation}
      ``Observation, reason and experimentation make up what we call the scientific method.''
\end{quotation}
\begin{flushright}
      - Richard P. Feynman
\end{flushright}

So far, this dissertation has provided background information on \acfp{ANN}, \index{heuristic}heuristics, \acf{HH} and probability theory in Chapters \ref{chap:anns}-\ref{chap:probability}. Chapter \ref{chap:bhh} provided the detail of the implementation of the proposed \acs{BHH} with all its components and hyper-parameters. Scientific experimentation can now be conducted. Chapter \ref{chap:introduction} identified a set of empirical goals for this dissertation. The goals of this dissertation include an empirical evaluation of the \acs{BHH}, its behaviour and performance, and a comparison to state of the art low-level \index{heuristic}heuristics. This chapter provides the detailed specification of the methodology that is followed for the empirical process. Details are provided on the implementation of experiments, datasets, selection of hyper-parameters and design decisions. The process by which the results are statistically analysed are also presented. The remainder of the chapter is structured as follows:

@@

These empirical tests represent a set of questions, related to the \acs{BHH}, that need to be answered. The empirical process is designed to answer these questions. The empirical process is structured as follows.

@@

Details on how the datasets where preprocessed and prepared is given in Appendix \ref{app:datasets}. The concept of class balancing is briefly discussed next.

@@

For the classification problems presented in Tables \ref{tab:methodology:datasets:classification} and \ref{tab:methodology:models:configurations}, the softmax activation function is added after training and is not included in the model during training. The loss functions, \acf{SparseCatXE} and \acf{BinXE}, that are used, contain a \index{softmax}softmax function.

@@

Note that from Table \ref{tab:methodology:heuristics}, values that are configured to make use of a decay schedule are presented with the initial value first and the decay rate in brackets next to it. The number of steps is the total number of mini-batch training steps that are executed for that particular dataset.

@@

In Figure \ref{fig:methodology:heuristics:proxies}, cells containing \textbf{x}, indicate that the associated \index{heuristic}heuristic implements that particular state parameter explicitly, and cells containing \textbf{o} indicate that the state parameter is implicitly implemented as part of the \acs{BHH} algorithm. The required mapping of proxied \index{heuristic}heuristic state operations is then implemented as a lookup of the table presented in Figure \ref{fig:methodology:heuristics:proxies}.

@@

In Table \ref{tab:methodology:bhh_baseline_configuration}, the \index{heuristic}heuristic pool configuration that is used, is referred to as \textit{all}. The \textit{all} configuration refers to a configuration where the \index{heuristic pool}heuristic pool contains all the low-level \index{heuristic}heuristics as presented in Section \ref{sec:methodology:heuristics}, including all gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics.

@@

In Table \ref{tab:methodology:experiments:bhh_variants}, the \index{heuristic pool}heuristic pool configuration \textit{gd} refers to the \index{heuristic pool}heuristic pool configuration where only gradient-based \index{heuristic}heuristics are included, and \textit{mh} refers to the \index{heuristic pool}heuristic pool configuration where only meta-heuristics are included.
